% Cover letter using letter.cls
% default is 10 pt
\documentclass[11pt]{letter} 

%\usepackage{helvetica}             % uses helvetica postscript font (download helvetica.sty)
\usepackage{newcent}                % uses new century schoolbook postscript font 
\usepackage{comment}    
\usepackage[colorlinks=false]{hyperref}

% the following commands control the margins:
\topmargin=-1in                     % Make letterhead start about 1 inch from top of page
\textheight=8.5in                   % text height can be bigger for a longer letter
\oddsidemargin=0pt                  % leftmargin is 1 inch
\textwidth=6.5in                    % textwidth of 6.5in leaves 1 inch for right margin

%\newenvironment 
\begin{document}

\signature{Guangfu Shi}             % name for signature 
\longindentation=0pt                % needed to get closing flush left
\let\raggedleft\raggedright         % needed to get date flush left

\newenvironment{myitemize}{\begin{itemize} % 
        \setlength{\itemsep}{0.25em} 
        \setlength{\topsep}{\itemsep} 
        \setlength{\labelsep}{1em}
        \setlength{\parskip}{0em}
        \setlength{\partopsep}{0em}
}%
{ \end{itemize} }

% Contact Person Information
\newcommand{\clcontactnamedefault}  {Hiring Manager} 
\newcommand{\clcontacttitle}        {}
\newcommand{\clcontactname}         {\clcontactnamedefault}  

\newcommand{\clcontactposition}     {}

% Company Information
\newcommand{\clcompanyname}         {}
\newcommand{\clcompanyaddr}         {}
\newcommand{\clcompanycity}         {} 
\newcommand{\clcompanyprov}         {}
\newcommand{\clcompanyzip}          {} 

% Job Information
\newcommand{\cljobpostedtitle}      {}
\newcommand{\cljobposteddate}       {}
\newcommand{\cljobpostedplace}      {}


% Personal Information
\newcommand{\clmyname}              {Guangfu Shi}
\newcommand{\clmyaddr}              {512-1625 Maisonneuve West\\Montreal, Quebec\\H3H 2N4}
\newcommand{\clmyemail}             {\href{mailto:stevegocoding@gmail.com}{stevegocoding@gmail.com}}
\newcommand{\clmyphone}             {(514) 583-0603}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 

\begin{letter}{
    \clcontacttile\ \clcontactname  \\
    \clcontactposition              \\
    \clcompanyname                  \\
    \clcompanyaddr                  \\
    \clcompanycity,\ \clcompanyprov \\
    \clcompanyzip} 

\begin{center}
\large\bf 
\clmyname                           \\ 

\clmyaddr                           \\
\clmyemail                          \\
\clmyphone
\end{center} 

\vfill % forces letterhead to top of page
 
\opening{Dear \clcontacttitle\ \clcontactname:} 

Your opening position of \cljobpostedtitle advertised on \cljobposteddate at \cljobpostedplace really caught my eye. This sounds like an exciting opportunity for me and I would appear to closely fit the candidate requirement as detailed in your ad. Therefor I am submitting my resume and would appreciate the chance to gain more insight into this position through personal discussion with you.      

I am currently finishing my graduate study focus on the field of Computer Graphics at Concordia University and expect to graduate in Fall. I have been interested in Computer Graphics, especially in 3D real-time rendering and game development since my undergraduate study. My academic experience has provided me with necessary knowledge and skills to become an effective 3D graphics/game engine programmer. Armed by the solid fundamental knowledge including 3D Mathematics, algorithms/data structure and the key skills such as proficiency in C/C++ programming language and OpenGL/Direct3D rendering API, I become capable of acquiring more diversified and extensive programming experience 3D real-time rendering and game development. By carefully reviewing the requirements of this position, I believe that I am well-qualified for this opportunity the following listing highlights the qualifications:

\begin{myitemize}
    
    \item Have object-oriented design principles, design patterns well-understood and be capable of programming in C++ proficiently.  
    \item Have development experience on a variety platforms including XBox360 and iPhone. 
    \item Be capable of modeling and manipulate data with solid knowledge of data structures and implementation ability using object-oriented language. 
    \item Good understanding of the whole game development process and the working context as a middleware developer for games.    
      
\end{itemize}

I believe that my background has provided me with a solid foundation for a future at \clcompanyname. Please review my accomplishments as highlighted on the enclosed resume. Should you agree I am well-qualified for this position. I would look forward to the opportunity of meeting with you personally to further explore your specific requirements and my qualifications. If you have any questions or concerns regarding my resume, please contact me at \clmyphone or \clmyemail.

Thank you for your time and consideration, 

\closing{Sincerely yours,}

\end{letter}
\end{document}
