\documentclass[10pt]{article}

\usepackage{charter}
\usepackage{fullpage}
\usepackage[colorlinks=false]{hyperref}
\usepackage{currvita}
\usepackage[top=0.9in, bottom=0.8in, left=1.25in, right=1.25in]{geometry}

\newenvironment{mylist}{%
    \begin{list}{}
        \setlength{\itemsep}{0.25em}%
        \setlength{\parsep}{0em}%
        \setlength{\topsep}{\itemsep}%
        \setlength{\parskip}{0em}%
        \setlength{\labelwidth}{0.1em}
    }
{ \end{list} }

\newenvironment{mydescription}{%
    \begin{description}
        \setlength{\itemsep}{0.25em}%
        \setlength{\parsep}{0em}%
        \setlength{\topsep}{\itemsep}%
        \setlength{\parskip}{0em}%
        \setlength{\labelwidth}{0.1em}
        \setlength{\labelsep}{0em} 
    }%
{\end{description}}

\newenvironment{myitemize}{\begin{itemize} % 
        \setlength{\itemsep}{0.25em} 
        \setlength{\topsep}{\itemsep} 
        \setlength{\labelsep}{1em}
        \setlength{\parskip}{0em}
        \setlength{\partopsep}{0em}
}%
{ \end{itemize} }
       
\pagestyle{empty}

\begin{document} 
\date{}
\newlength{\oldcvlabelwidth}
\newlength{\oldcvlabelsep}

%\small



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% This section is the head of the resume
\begin{cv} {{\large Guangfu Shi}\\
    { \normalsize \mdseries 29-2105 Rue Chomedey, Montreal, Quebec, Canada. H3H 2A8\\ 
    Phone: {\mdseries (514)583-0603}  
    \hfill E-mail: {\mdseries \href{mailto:stevegocoding@gmail.com} {stevegocoding@gmail.com}}
    }
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setlength{\oldcvlabelwidth}{\cvlabelwidth}
\setlength{\oldcvlabelsep}{\cvlabelsep}
\setlength{\cvlabelwidth}{0.5em}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This section is the RESUME PROFILE
%\input{resume_profile_test}

\begin{cvlist}{Profile} 
\item
    \begin{myitemize}
        \item Graduate in Computer Science, interested in computer graphics, game development and system development.
        \item Development experience on a variety of platforms including XBox360 and iPhone.
        \item Solid mathematics (trigonometry, calculus, and linear algebra) and algorithms skills. 
        \item Excellent communication skill and teamwork ability. 

    \end{myitemize}
\end{cvlist}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setlength{\cvlabelwidth}{1em}
%\setlength{\oldcvlabelsep}{\cvlabelsep}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This section is all about EDUCATION
\begin{cvlist}{Education}
    
    \item   \textbf{M.S., Computer Science} \hfill 2011 \\ 
            \emph{Concordia University, Montreal, Canada}
    \item   \textbf{BEng, Software Engineering} \hfill 2007 \\
            \emph{Beijing Jiaotong University, Beijing, China. GPA: 4.0/4.0}
\end{cvlist}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{cvlist}{Technical Skills}
\item
    \begin{mydescription} 
        \item[Develop Platform] \hfill \\
            MS Windows, Linux, MacOS X, iOS, XBox 360.
        \item[Programming Language] \hfill \\
            C/C++, Objective-C, C\#, JavaScript, Java, Lua, Python, GLSL, CUDA, Cg.
        \item [Engines/Frameworks/API] \hfill \\
            Unity, Ogre3D, PhysX, XNA, Qt, OpenGL/GL ES, DirectX, Cocoa, Boost.
        \item[Development Tools] \hfill \\
            Visual Studio, XCode, GCC, VIM, 3ds Max, Subversion, Git, CMake.
    \end{mydescription} 
\end{cvlist} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\setlength{\cvlabelwidth}{0em}
%\setlength{\cvlabelsep}{\labelsep}
%\setlength{\oldcvlabelsep}{\cvlabelsep}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This section is all about EXPERIENCE 
\begin{cvlist}{Technical Experience}
\item
    \begin{mydescription}
        %% Projects and demos
        \item[Golf Simulator]  (In progress) \hfill \\
            Working on a real-time golf simulator using Ogre3D as rendering engine and powered by PhysX for physics simulation. A Qt-based golf course editor is being implemented as well.

        \item[Graduate Research Project: GPU KD-Tree Constructor for Ray Tracing] \hfill \\
            Focus on the approaches of accelerating ray-tracing rendering mainly utilizing the kd-tree structure and GPU implementation. Using \LaTeX\ for report and thesis.

        \item[3D First Person Shooter Game Demo] \hfill \\
            Developed a FPS game demo using C++ and Direct3D 9, implemented outdoor terrain rendering with level of detail, key frame animation (MD3 format) and particle system.

        \item[2D Super Mario Game] \hfill \\
            Implemented a 2D sprite-based super mario game using C++ and DirectDraw, a level editor has been developed as well using C\# and XML file for the data storage.

        \item[3D Racing Game Demo] \hfill \\ 
            Created An OpenGL racing game demo, with texture mapping, GLSL, particle system and billboards.

        %\item[A J2ME game] \hfill \\
        %    Designed and implemented a ``3 in 1'' games collection using Java and J2ME.

        \item[Model Exporter for 3ds Max] \hfill \\
            Implemented customized 3D model format exporter for 3ds Max using MAXScript.
    \end{mydescription}
\end{cvlist}

\begin{cvlist}{Internship Experience}
\item 
    \begin{mydescription}
        \item[Offshore Development Center, VanceInfo, Beijing, China] \hfill Winter,2007 \\ 
            Responsible for writing testing scripts for Microsoft products. 
    \end{mydescription}
\end{cvlist}

\begin{cvlist}{Teaching Assistant Experience}
\item
    \begin{mydescription}
        \item[Lab instructor, \emph{Game Design and Implementation}, Concordia University] \hfill Fall 2009\\
            Assist students to implement their game designing on Xbox 360 console. 

        \item[Teaching assistant, \emph{Advanced Computer Graphics}, Concordia University] \hfill Winter 2009 \\
            Assist students to finish the assignments and project using OpenGL. 
    \end{mydescription}
\end{cvlist}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\setlength{\cvlabelsep}{\labelsep}
%\setlength{\oldcvlabelsep}{\cvlabelsep}
\begin{center}
    \textbf{Reference Available Upon Request}
\end{center}

\end{cv} 
\end{document}
